---
title: "Supplementary Methods 1"
author: "Chris Terry"
output:
  pdf_document: 
    toc: yes
    number_sections: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Summary 

This document is a knit `.rmd` file that works through the steps of the reanalysis of *Small rainfall changes drive substantial changes in plant coexistence* by Van Dyke et al 2022  (Nature), to support a 'Matters Arising' response. Original data from the authors is available at https://doi.org/10.5281/zenodo.7083314 

Section 4 details the methods used to conduct a model comparison analysis to examine the level of statistical support for the treatment impacting the key model parameters and subsequent key coexistence quantities.  

Section 5 propogates forward the authors original full bootstrap through to the final assessment of whether the predicted coexistence outcome species pair differs between treatments. 


# Loading and looking at data
```{r message = FALSE, warning = FALSE}
library(tidyverse)
set.seed(1)

Path_to_Orig <- '../DroughtCompUncertainty/water_competition-2.0/Sedgwick_public/'

nls_boot_pairs<-read.csv(paste0(Path_to_Orig,"output/nls_boot_pairs_1000_full_model.csv"))
seed_data <- read.csv(paste0(Path_to_Orig,"data/drought_seed_production_data.csv"))

seed_data$Tr <- ifelse(seed_data$treat == "W", 1, 2)
seed_data <- seed_data %>% 
  mutate( background = ifelse(is.na(background),
                              focal, background)) # where 0 background, naming after focal

seed_data$N_acwr <- ifelse(seed_data$background == "ACWR", seed_data$num_comp, 0)
seed_data$N_femi <- ifelse(seed_data$background == "FEMI", seed_data$num_comp, 0)
seed_data$N_homu <- ifelse(seed_data$background == "HOMU", seed_data$num_comp, 0)
seed_data$N_pler <- ifelse(seed_data$background == "PLER", seed_data$num_comp, 0)
seed_data$N_saco <- ifelse(seed_data$background == "SACO", seed_data$num_comp, 0)
seed_data$N_urli <- ifelse(seed_data$background == "URLI", seed_data$num_comp, 0)
```

## How much data? 

```{r}
nrow(seed_data)
count(seed_data, background, focal, treat) %>% arrange(n) %>% head()
```

## How much uncertainty in types of parameters

```{R}

### no lambda sd saved, so will need to reconstruct, following original code

spp_treat_boot_combos <-read.csv(paste0(Path_to_Orig, "output/final_output_nls_boot_1000.csv")) 

#Data frame with medians and sds for parameters----
spp_list <- sort(na.omit( unique(seed_data$focal)))
treat_list <- sort( na.omit( unique(seed_data$Tr)))
spp_treat_combos <- expand.grid(species = spp_list, treatment = treat_list)
comp_labels <- sort( na.omit( unique(seed_data$background) ))

spp_treat_boot_combos$sp_pair <- paste(spp_treat_boot_combos$focal,
                                       spp_treat_boot_combos$competitor, sep = "_")

spp_treat_comp_combos <- expand.grid(focal = spp_list,
                                     competitor = comp_labels,
                                     treatment = treat_list)

boot_NEW <- spp_treat_comp_combos %>%  mutate(alpha = 0, alpha_sd = 0,
         lambda = 0, lambda_sd =0)
boot_NEW$sp_pair <- paste(boot_NEW$focal, boot_NEW$competitor, sep = "_")  

for( i in 1:nrow(spp_treat_comp_combos)) {
  sp1 <- spp_treat_comp_combos[i, "focal"] %>% unlist
  sp2 <- spp_treat_comp_combos[i, "competitor"] %>% unlist
  treatt <- spp_treat_comp_combos[i , "treatment"] %>% unlist
  boot_NEW[i, "alpha"] <- median(with(spp_treat_boot_combos, 
                                      alpha[treatment == treatt &
                                              focal == sp1 &
                                              competitor == sp2 
                                      ]), na.rm=TRUE)
  boot_NEW[i, "alpha_sd"] <- sd(with(spp_treat_boot_combos, 
                                     alpha[treatment == treatt & 
                                             focal == sp1 & 
                                             competitor == sp2 
                                     ]), na.rm=TRUE)
  boot_NEW[i, "lambda"] <- median(with(spp_treat_boot_combos, 
                                       lambda[focal == sp1 & competitor == sp2 & 
                                                treatment == treatt]), na.rm=TRUE)
  boot_NEW[i, "lambda_sd"] <- sd(with(spp_treat_boot_combos, 
                                      lambda[focal == sp1 & competitor == sp2 & 
                                               treatment == treatt]), na.rm=TRUE)
} 

boot_NEW %>%
  filter(focal==competitor ) %>%
  mutate(LamCV= lambda_sd/lambda) %>%
  summarise(mean(LamCV))

boot_NEW %>%
  mutate(AlpCV= alpha_sd/alpha)%>%
  summarise(mean(AlpCV))

```


# Plotting raw data with model best-fit


```{r}
spp_list <- sort(na.omit( unique(seed_data$focal)))
```


```{r}
set.seed(3)

AddPreds<- function(focalsp){
  focal_data <- filter(seed_data, focal == focalsp)
  
  fit<- nls(log(num_seeds)~log(lambda[Tr]/(1+a_ACWR[Tr]*N_acwr+a_FEMI[Tr]*N_femi+
                                             a_HOMU[Tr]*N_homu+a_PLER[Tr]*N_pler+
                                             a_SACO[Tr]*N_saco+a_URLI[Tr]*N_urli)),
            data=focal_data, 
            start=list('lambda'= c(100,100),
                       a_ACWR=c(0.1, 0.1), a_FEMI=c(0.1, 0.1), 
                       a_HOMU=c(0.1, 0.1), a_PLER=c(0.1, 0.1), 
                       a_SACO=c(0.1, 0.1),a_URLI=c(0.1, 0.1)),
            lower = c( 1, 1, rep(.001, 12) ),
            upper = c(10000, 10000, rep(2, 12)), 
            control = list(maxiter = 100000),
            algorithm = 'port') 
  focal_data$Prediction <- predict(fit)
  return(focal_data)
}

data_predict <- map_df( spp_list,AddPreds)
```


```{r fig.height=8, fig.width=8}
data_predict %>%
  rename(Focal = focal, Background = background) %>%
  arrange(num_comp)%>%
  ggplot(aes( x =num_comp, col = treat)) +
  geom_point(aes(y = log(num_seeds)), size = 1)+
  facet_grid(Focal~Background, scales = 'free_x',
             labeller= label_both)+
  geom_line(aes(y = Prediction))+
  theme_light()+
  xlab('Number of Competitors')+
  ylab('Number of Seeds produced (log scale)')+
  scale_color_manual(values=c('W' ="#4E84C4", 'D' = "#D16103"),
                     name = "Treatment:", 
                     labels = c("Ambient", "Reduced Rain"))+
  theme(legend.position = 'bottom')


ggsave('ExFig1_RawPredict.png', height = 8, width = 8, dpi = 200)


```       


# Fitting set of models with different levels of parameterisation

```{r warning = FALSE}
## Mapping over all 6 focal species
FindFourAICs <- function(focalsp){
  
  focal_data <- filter(seed_data, focal == focalsp)
  
  fit_test<- nls(log(num_seeds)~log(lambda[Tr]/(1+a_ACWR[Tr]*N_acwr+a_FEMI[Tr]*N_femi+
                                                  a_HOMU[Tr]*N_homu+a_PLER[Tr]*N_pler+
                                                  a_SACO[Tr]*N_saco+a_URLI[Tr]*N_urli)),
                 data=focal_data, 
                 start=list('lambda'= c(100,100),
                            a_ACWR=c(0.1, 0.1), a_FEMI=c(0.1, 0.1), 
                            a_HOMU=c(0.1, 0.1), a_PLER=c(0.1, 0.1),
                            a_SACO=c(0.1, 0.1),a_URLI=c(0.1, 0.1)),
                 lower = c( 1, 1, rep(.001, 12) ),
                 upper = c(10000, 10000, rep(2, 12)), 
                 control = list(maxiter = 100000),
                 algorithm = 'port') 
  
  fit_test_nosplit<- nls(log(num_seeds)~log(lambda/(1+a_ACWR*N_acwr+a_FEMI*N_femi+
                                                      a_HOMU*N_homu+a_PLER*N_pler+
                                                      a_SACO*N_saco+a_URLI*N_urli)),
                         data=focal_data, 
                         start=list('lambda'= c(100),
                                    a_ACWR=c(0.1), a_FEMI=c(0.1), 
                                    a_HOMU=c(0.1), a_PLER=c(0.1),
                                    a_SACO=c(0.1),a_URLI=c(0.1)),
                         lower = c( 1, rep(.001, 6) ),
                         upper = c(10000, rep(2, 6)), 
                         control = list(maxiter = 100000),
                         algorithm = 'port')
  
  fit_test_justA<- nls(log(num_seeds)~log(lambda/(1+a_ACWR[Tr]*N_acwr+a_FEMI[Tr]*N_femi+
                                                    a_HOMU[Tr]*N_homu+a_PLER[Tr]*N_pler+
                                                    a_SACO[Tr]*N_saco+a_URLI[Tr]*N_urli)),
                       data=focal_data, 
                       start=list('lambda'= c(100),a_ACWR=c(0.1, 0.1), a_FEMI=c(0.1, 0.1), 
                                  a_HOMU=c(0.1, 0.1), a_PLER=c(0.1, 0.1),
                                  a_SACO=c(0.1, 0.1),a_URLI=c(0.1, 0.1)),
                       lower = c( 1, rep(.001, 12) ),
                       upper = c(10000, rep(2, 12)), 
                       control = list(maxiter = 100000),
                       algorithm = 'port')
  
  fit_test_justLam<- nls(log(num_seeds)~log(lambda/(1+a_ACWR[Tr]*N_acwr+a_FEMI[Tr]*N_femi+
                                                      a_HOMU[Tr]*N_homu+a_PLER[Tr]*N_pler+
                                                      a_SACO[Tr]*N_saco+a_URLI[Tr]*N_urli)),
                         data=focal_data,
                         start=list('lambda'= c(100,100),a_ACWR=c(0.1, 0.1), a_FEMI=c(0.1, 0.1), 
                                    a_HOMU=c(0.1, 0.1), a_PLER=c(0.1, 0.1),
                                    a_SACO=c(0.1, 0.1),a_URLI=c(0.1, 0.1)),
                         lower = c( 1,1, rep(.001, 12) ),
                         upper = c(10000,10000, rep(2, 12)), 
                         control = list(maxiter = 100000),
                         algorithm = 'port')
  
  XX <- data.frame(FocalSp = focalsp,
                   LogL_NoTre = logLik(fit_test_nosplit),
                   LogL_JustA = logLik(fit_test_justA),
                   LogL_JustL = logLik(fit_test_justLam),
                   LogL_Orig  = logLik(fit_test)) %>%
    mutate(k_NoTre =7, 
           k_JustA =13,
           k_JustL =8,
           k_Orig = 14)%>%
    mutate(aic_NoTre = 2*k_NoTre - (2*LogL_NoTre) ,
           aic_JustA = 2*k_JustA - (2*LogL_JustA) ,
           aic_JustL = 2*k_JustL - (2*LogL_JustL) ,
           aic_Orig  = 2*k_Orig  - (2*LogL_Orig))
  
return(XX)
}
```

## AIC Tables
```{R warning = FALSE}
AICTable<- map_df( spp_list, FindFourAICs)



knitr::kable(t(AICTable), digits = 1)

knitr::kable(select(AICTable,FocalSp , starts_with('aic')), digits = 1)


dfLL <- data.frame(LogLik = select(AICTable, starts_with('LogL')) %>%
                     summarise_all(sum) %>% t) 


dfLL$n_params = c(84, 42, 78, 48)

dfLL %>%
  mutate( AIC= (2*n_params) - (2*LogLik) )


```

# Full Posteriors

### Which pair-directions to plot?
```{r}
#get all the pairs where the fitness difference is above 1 in the wet plots----
nls_boot_pairs$fd_superior <- ifelse(nls_boot_pairs$fd < 1, 1/nls_boot_pairs$fd, nls_boot_pairs$fd)
nls_boot_pairs$fd_sup_sp <- ifelse(nls_boot_pairs$fd <= 1, 1, 2)
nls_boot_pairs_sup <- nls_boot_pairs %>%filter(fd_sup_sp == 2 )
W_superior <- with(nls_boot_pairs_sup, sp_pair[treatment==1])

boots_pairs_w_sup <- nls_boot_pairs %>% filter(sp_pair %in% W_superior)
boots_pairs_w_sup$treat <- factor(boots_pairs_w_sup$treat, levels = c(1, 2))

boots_pairs_w_sup$treatment <- factor(boots_pairs_w_sup$treatment, levels = c(1, 2))
boots_pairs_w_sup$label <- paste0(substr(boots_pairs_w_sup$focal, 1, 2),
                                  "-", substr(boots_pairs_w_sup$competitor, 1, 2))

PairsToPlot <- unique(boots_pairs_w_sup$sp_pair )

```

### Data Preparation
```{R}
final_output_nls_boot <-read.csv(paste0(Path_to_Orig,
                                        "output/final_output_nls_boot_1000.csv"))
spp_treat_boot_combos <- final_output_nls_boot 

#Data frame with medians and sds for parameters----
spp_list <- sort(na.omit( unique(seed_data$focal)))
treat_list <- sort( na.omit( unique(seed_data$Tr)))
spp_treat_combos <- expand.grid(species = spp_list, treatment = treat_list)
comp_labels <- sort( na.omit( unique(seed_data$background) ))

spp_treat_boot_combos$sp_pair <- paste(spp_treat_boot_combos$focal,
                                       spp_treat_boot_combos$competitor, sep = "_")  

spp_treat_comp_combos <- expand.grid(focal = spp_list,
                                     competitor = comp_labels,
                                     treatment = treat_list)

nls_boot_pairs$sp_pair <- paste(nls_boot_pairs$focal, nls_boot_pairs$competitor, sep = "_")  

nls_boot_pairs %>%
  filter(sp_pair %in% PairsToPlot) %>%
  mutate( Treatment = ifelse(treatment ==1, 'WET', 'DRY')) ->  OriginalErrorBarsForAdding

```

### Create coexistence area for plot - min/max fitness difference that permits coexistence

```{r}
niche_differentiation <- seq(from = -.25, to = 1, by = 0.001)
niche_overlap <- 1-niche_differentiation
fitness_ratio_min <- niche_overlap
fitness_ratio_max <- 1/niche_overlap

coexistarea_df <- data.frame(niche_diff = niche_differentiation,
                             min_fitness_ratio = fitness_ratio_min,
                             max_fitness_ratio = fitness_ratio_max)
```


## Plotting
```{R fig.height=10, fig.width=10, warning = FALSE}
spp_treat_boot_combos %>%
  filter(sp_pair %in% PairsToPlot) %>%
  mutate( Treatment = ifelse(treatment ==1, 'WET', 'DRY')) %>%
  arrange(snd) %>%
  ggplot()+
  geom_line(data = coexistarea_df, aes(x = niche_diff, y = max_fitness_ratio)) +
  geom_line(data = coexistarea_df,  aes(x = niche_diff, y = min_fitness_ratio)) +
  geom_ribbon(data = coexistarea_df, aes(x = niche_diff, ymin = min_fitness_ratio,
                                         ymax = max_fitness_ratio), fill = 'grey80') +
  geom_point(aes( x = snd, y = fd,col = Treatment), alpha = 0.1, size = 0.1)+
  facet_wrap(~sp_pair,  nrow = 3)+
  scale_y_log10()+
  coord_cartesian(xlim = c(-0.2,1), ylim = c(0.01, 100) )+ 
  theme_classic()+
  geom_point(aes(x = snd, y = fd, color = Treatment),
             data= OriginalErrorBarsForAdding) +
  geom_errorbar(aes(x = snd, ymin = fd_low, ymax = fd_high),
                data= OriginalErrorBarsForAdding) +
  geom_errorbarh(aes(y = fd, xmin = snd_low, xmax =snd_high),
                 data= OriginalErrorBarsForAdding)+
  scale_color_manual(values=c('WET' ="#4E84C4", 'DRY' = "#D16103"), 
                     name = "Treatment:",
                     labels = c("Ambient", "Reduced Rain"))+
  theme(legend.position = 'bottom', axis.text.x = element_text(angle = -90))+
  ylab('Maximum Fitness Ratio')+
  xlab('Stabilising Niche Difference')

ggsave('ExFig2_CoexistPlots.png', height = 10, width = 8, dpi = 200)

```

## Determining fraction of pairs that follow identified pattern
```{r}
# original results
nls_boot_pairs_unique <-  nls_boot_pairs %>%  filter(focal != competitor )
nls_boot_pairs_unique$treatment <- factor(nls_boot_pairs_unique$treatment, levels = c(1, 2))
nls_boot_pairs_unique$fd_superior <- ifelse(nls_boot_pairs_unique$fd < 1, 
                                            1/nls_boot_pairs_unique$fd,
                                            nls_boot_pairs_unique$fd)
nls_boot_pairs_unique$coexist <- ifelse((nls_boot_pairs_unique$snd > 
                                           (1-1/nls_boot_pairs_unique$fd_superior)),
                                        1, 0 )

##Stabilizing niche and fitness differences: (Table ED3)
pars_boot <- nls_boot_pairs_unique %>%
  select(focal,competitor,treatment,snd,
         fd,fd_superior,coexist, fd_sup_sp)

pars_boot$species <- paste0(substr(pars_boot$focal, 1, 2),
                            "-",
                            substr(pars_boot$competitor, 1, 2))

pars_boot$outcome <- ifelse(pars_boot$coexist == 1, "coexist",
                            ifelse(pars_boot$fd_sup_sp == 2, 
                                   paste0(substr(pars_boot$species, 4, 5), " wins"), 
                                   paste0(substr(pars_boot$species, 1, 2), " wins")))

pair_labels <- pars_boot %>%
  filter(treatment == 1 ) %>%
  filter(fd > 1)

pair_labels <- unique(pair_labels$species)
pars_boot <- pars_boot %>% filter(species %in% pair_labels)
pars_boot <- subset(pars_boot, select =  -c(focal, competitor, coexist,
                                            fd_sup_sp, fd_superior))

pars_boot_wide<-pivot_wider(data = pars_boot,
                            names_from = treatment,
                            values_from = c(snd, fd, outcome))%>%
  arrange(species)

```

## Repeating across the whole bootstrap sample
```{r}
spp_treat_boot_combos %>%
  filter(sp_pair %in% PairsToPlot) %>%
  mutate(fd_superior <- ifelse(fd < 1, 1/fd,fd) ,
         fd_sup_sp <- ifelse(fd <= 1, 1, 2),
         coexist = ifelse((snd > (1-1/fd_superior)), 1, 0 ),
         outcome = ifelse(coexist == 1, "coexist",
                          ifelse(fd_sup_sp == 2, 
                                 paste0(focal , " wins"), 
                                 paste0(competitor , " wins")))) %>%
  group_by(treatment, sp_pair) %>%
  count(outcome) %>%
  pivot_wider(id_cols = c(treatment, sp_pair), names_from = outcome, 
              values_from = n, values_fill = 0) -> PosteriorResults

## Just looking at change in 'coexist' result

PosteriorResults %>%
  mutate( Treatment = ifelse(treatment ==1, 'WET', 'DRY'))%>%
  mutate(coexist_frac = coexist/1000) %>%
  ungroup() %>%
  select(Treatment, sp_pair, coexist_frac) %>%
  pivot_wider(id_cols = sp_pair, names_from = Treatment, values_from = coexist_frac) %>%
  mutate( AbsoluteChange = WET-DRY) %>%
  mutate(species  = paste0(substr(sp_pair     , 1, 2),## For Joining with pars_boot_wide
                           "-",
                           substr(sp_pair     , 6, 7))) %>%
  left_join(pars_boot_wide, by = "species") -> JoinResults


JoinResults$OriginalFindsChange <- JoinResults$outcome_1 != JoinResults$outcome_2


## probability of each draw showing switch from coexistence = prob(coexist1) *prob 
## Assuming just two outcomes: coexist, or something else
# If change from victory -> coexist, probability observe change =  1-prob(coexist1) * prob(coexist)
# If change from coexist -> victory, probability observe change =  prob(coexist1) * 1-prob(coexist)

JoinResults %>%
  filter(OriginalFindsChange) %>%
  mutate(LikelihoodObserveChange = ifelse(outcome_1 == 'coexist',
                                          WET *(1-DRY),
                                          (1-WET)*DRY)) %>%
  select(SpeciesPair =species, 
         LikelihoodCoexist_Wet= WET,
         LikelihoodCoexist_Dry = DRY,
         outcome_Wet=outcome_1, outcome_Dry=outcome_2,
         LikelihoodObserveChange )-> JoinResults2

knitr::kable(JoinResults2,digits =3)

JoinResults2$LikelihoodObserveChange %>% mean
```


# Session Info

```{r}
sessionInfo()
```
